### 2020-08-26 cases_and_policies/rmd/cf-pindex.Rmd

@@

L <- 14
sdf <- subset(df, df$date>=datelims[1]) #+L)
regs <- mainregressions(sdf,
                        "dlogdc", pols, bvars, infovars, tvars, xlist, ilist, iv, L=L)
m <- regs$piy[[1]]$reg
cnames <- c(pols, infovars[[1]])
di <- dieff_table(lapply(regs$pib[[1]][1:4], function(x) x$reg$coef[,1]),
                  regs$pbiy[[1]]$reg$coef[,1],
                  regs$piy[[1]]$reg$coef[,1],
                  policies=cnames)

@@

S <- 999
bs <- bootstrap_felm(sdf, c(pib,list(pbiy,piy)), S=S)
bdi <- lapply(1:S, function(i)
  dieff_table(lapply(1:4, function(j) bs[[j]][,i]),
              bs[[5]][,i], bs[[6]][,i],
              policies=cnames)
  )

@@

L <- 21
sdf <- subset(df, df$date>=datelims[1]) #+L)
regs <- mainregressions(sdf,
                        "dlogdd", pols, bvars, infovars, tvars, xlist, ilist, iv, L=L)

@@

cnames <- c(pols, infovars[[1]])
di <- dieff_table(lapply(regs$pib[[1]][1:4], function(x) x$reg$coef[,1]),
                  regs$pbiy[[1]]$reg$coef[,1],
                  regs$piy[[1]]$reg$coef[,1],
                  policies=cnames)

>>>>

```{r testsmooth, cache=FALSE}
source("smoothtests.R")
```

@@

L <- 14
sdf <- subset(df, df$date>=datelims[1]) #+L)
regs <- mainregressions2(sdf,
                        "dlogdc", pols, bvars, infovars, tvars, xlist, ilist, iv, L=L)
m <- regs$piy[[1]]$reg
cnames <- c(pols, infovars[[1]])
di <- dieff_table2(lapply(regs$pib[[1]][1:4], function(x) x$reg$coef[,1]),
                  regs$pbiy[[1]]$reg$coef[,1],
                  regs$piy[[1]]$reg$coef[,1],
                  policies=cnames)

@@

S <- 999
bs <- bootstrap_felm2(sdf, c(pib,list(pbiy,piy)), S=S)
bdi <- lapply(1:S, function(i)
  dieff_table2(lapply(1:4, function(j) bs[[j]][,i]),
               bs[[5]][,i], bs[[6]][,i],
               policies=cnames)
  )

@@

L <- 21
sdf <- subset(df, df$date>=datelims[1]) #+L)
regs <- mainregressions2(sdf,
                        "dlogdd", pols, bvars, infovars, tvars, xlist, ilist, iv, L=L)

@@

cnames <- c(pols, infovars[[1]])
di <- dieff_table2(lapply(regs$pib[[1]][1:4], function(x) x$reg$coef[,1]),
                  regs$pbiy[[1]]$reg$coef[,1],
                  regs$piy[[1]]$reg$coef[,1],
                  policies=cnames)

### 2020-08-26 cases_and_policies/rmd/counterfactuals.Rmd

# Data Preparation
```{r setup, cache=FALSE, warning=FALSE, include=FALSE}

@@

@@

# ```{r otherstates, cache=TRUE, fig.cap="Effect of Removing Policies"}
# if (!knitr::is_latex_output()) {
#   for( st in c("New York", "Florida", "Michigan", "Georgia", "Massachusetts")) {
#     f <- cfplots(st, cfnop, data=df)
#     grid.arrange(f$figd, f$figdp, nrow=2, top =  textGrob(st,gp=gpar(fontsize=20, font=2)))
#     grid.arrange(f$figl, f$figp, nrow=2, top =  textGrob(st,gp=gpar(fontsize=20, font=2)))
#   }
# }
# ```

# ```{r nop-state-figures, cache=TRUE, warning=FALSE}
# states <- c("Washington","Illinois","Massachusetts")
# for(st in states) {
#   f <- cfplots(st, cfnop, data=df)
#
#   figdev(sprintf("%s/tex/tables_and_figures/%s-nop-dgrowth_v1.pdf",rootdir,st), width=5,height=3.75)
#   print(f$figdp)
#   dev.off()
#
#   figdev(sprintf("%s/tex/tables_and_figures/%s-nop-growth_v1.pdf",rootdir,st), width=5,height=3.75)
#   print(f$figd + ylim(c(-1,5)))
#   dev.off()
#
#   figdev(sprintf("%s/tex/tables_and_figures/%s-nop-cases_v1.pdf",rootdir,st), width=5,height=3.75)
#   print(f$figl)
#   dev.off()
#
#   figdev(sprintf("%s/tex/tables_and_figures/%s-nop-dcases_v1.pdf",rootdir,st), width=5,height=3.75)
#   print(f$figp)
#   dev.off()
# }
# ```

>>>>

# Data Preparation

```{r setup, cache=FALSE, warning=FALSE, include=FALSE}

@@

# stupid tidyverse stealing base package names ...
if("dplyr" %in% (.packages())){
  detach("package:dplyr", unload=TRUE)
}

@@

### 2020-08-26 cases_and_policies/rmd/datasummary.Rmd

```{r setup}
library(ggthemes)
library(ggplot2)
library(gridExtra)
library(knitr)
library(kableExtra)

@@

```{r gplots, cache=TRUE, warning=FALSE}
## fign <-
##   ggplot(aggregate(retail_and_recreation_percent_change_from_baseline
##                    ~ date,
##                    FUN=function(x) sum(!is.na(x)), data=cs)) +
##   geom_line(aes(x=date, y=retail_and_recreation_percent_change_from_baseline), size=1) +
##   ylab("Number non-missing") +
##   theme(legend.position = "none") +
##   xlab("") + plottheme + ggtitle("Number of non-missing observations of Google Mobility Reports") +
##   colors() + xlim(startday, max(cs$date))
## fign

quantileplot <- function(v, p=c(0.05, 0.25, 0.5, 0.75, 0.95), data=cs) {
  data$y <- data[,v]
  adf <- aggregate(y ~ date, data=data,
                   FUN=function(x) quantile(x, probs=p, na.rm=TRUE))
  p <- as.factor(p)
  s <- 1.2
  txt <- data.frame(date=max(adf$date), y=adf$y[nrow(adf$y),], p=p)
  names(adf)[1] <- "date"
  figm <- ggplot(adf) +
    geom_line(aes(x=date, y=adf$y[,1], color=p[1]), size=s) +
    geom_line(aes(x=date, y=adf$y[,2], color=p[2]), size=s) +
    geom_line(aes(x=date, y=adf$y[,3], color=p[3]), size=s) +
    geom_line(aes(x=date, y=adf$y[,4], color=p[4]), size=s) +
    geom_line(aes(x=date, y=adf$y[,5], color=p[5]), size=s) +
    geom_text(data=txt,aes(x=date,y=y,color=p, label=p,
                           hjust="left",vjust="center", size=2)) +
    plottheme + ylab("Percent Change") +
    colors() + ggtitle(TeX(paste("Evolution of",
                             varlabels[varlabels$Variable==v,"Label"]))) +
    geom_line(data=data, aes(x=date, y=y, group=state), alpha=0.2) +
    theme(legend.position="none") +
    #labs(color='Quantile')  +
    xlim(startday, max(data$date))
}

>>>>

```{r setup}
library(ggthemes)
library(ggplot2)
library(gridExtra)
library(knitr)
library(kableExtra)
library(latex2exp)
library(plm)
library(lubridate)

@@

```{r gplots, cache=FALSE, warning=FALSE}
## fign <-
##   ggplot(aggregate(retail_and_recreation_percent_change_from_baseline
##                    ~ date,
##                    FUN=function(x) sum(!is.na(x)), data=cs)) +
##   geom_line(aes(x=date, y=retail_and_recreation_percent_change_from_baseline), size=1) +
##   ylab("Number non-missing") +
##   theme(legend.position = "none") +
##   xlab("") + plottheme + ggtitle("Number of non-missing observations of Google Mobility Reports") +
##   colors() + xlim(startday, max(cs$date))
## fign

quantileplot <- function(v, p=c(0.05, 0.25, 0.5, 0.75, 0.95), data=cs) {
  data$y <- data[,v]
  adf <- aggregate(y ~ date, data=data,
                   FUN=function(x) quantile(x, probs=p, na.rm=TRUE))
  p <- as.factor(p)
  s <- 1.2
  txt <- data.frame(date=max(adf$date), y=adf$y[nrow(adf$y),], p=p)
  names(adf)[1] <- "date"
  figm <- ggplot(adf) +
    geom_line(aes(x=date, y=adf$y[,1], color=p[1]), size=s) +
    geom_line(aes(x=date, y=adf$y[,2], color=p[2]), size=s) +
    geom_line(aes(x=date, y=adf$y[,3], color=p[3]), size=s) +
    geom_line(aes(x=date, y=adf$y[,4], color=p[4]), size=s) +
    geom_line(aes(x=date, y=adf$y[,5], color=p[5]), size=s) +
    geom_text(data=txt,aes(x=date,y=y,color=p, label=p,
                           hjust="left",vjust="center", size=2)) +
    plottheme + ylab("Percent Change") +
    colors() + ggtitle(TeX(paste("Evolution of",
                             varlabels[varlabels$Variable==v,"Label"]))) +
    geom_line(data=data, aes(x=date, y=y, group=state), alpha=0.2) +
    theme(legend.position="none") +
    #labs(color='Quantile')  +
   # xlim(startday, max(data$date))
  xlim(startday,as.Date("2020-06-03"))
}
